### 2015-08-11 paper/manuscript/plos_template.tex
modify typos

Cancer is a genomic disease. 
As we lead a life, DNA within our cells acquires random somatic mutations,
mainly caused by DNA replication errors and exposures to mutagens such as chemical substances, radioactivities and inflammatory reactions.  
Although most mutations are harmless (called ``passenger mutations''), 
a small portions of mutations at some specific sites in cancer genes (``driver mutations'') 
%confer growth activities to the cells over other cells,
affect cell growth,
causing autonomous proliferation, tissue invasion, and contributing to oncogenesis \cite{stratton2009cancer}.
Cancer genome studies typically focus on identifying driver mutations, 
to help understand the mechanism of cancer development.
However, passenger mutations can also yield important information, 
because they often show patterns (``mutation signatures'') which 
can provide insights into the forces that cause somatic mutations.
%Classical analyses of mutation patterns have revealed a number of relationships between mutation patterns and carcinogens.
For example, classical studies of mutation patterns
revealed that C $>$ A mutations are abundant in lung cancers in patients with smoking history,
and these are caused by benzo(a)pyrene included in tobacco smokes \cite{pmid12379884}.
Also, C $>$ T and CC $>$ TT  mutations are abundant in ultraviolet-light-associated skin cancers, 
and these are caused by pyrimidine dimers as a result of ultraviolet radiation \cite{pmid15748635}.

@@

The inferred APOBEC signature under the independent model
shows a clear depletion of G base at the $-2$ position,
which is consistent to the previous study \cite{pmid23318258} and results in the next subsection ((Figs. 3A and 3B)).
In contrast, for the full model, this tendency is rather mild (Figs. 3C, 3D and S1).
The inferred AA mutation signature has no clear characteristics at the $-2$ position.
These results suggest that our independent model has the potential
to identify signatures in more detail and with less data than existing approaches based on the full model.

\begin{figure}[h]
\caption{{\bf The mutation signatures for the UCUT data, and the results of downsampling experiments.}
3072 elements in the full model mutation signatures were shown divided by 6 substitution patterns and strand directions.
(A) APOBEC signature for the independent model.
(B) AA signature for the independent model.
(C) APOBEC signature for the full model.
(D) AA signature for the full model.
(E) APOBEC signature stability.
(F) AA signature stability.}
\label{UCUT}
\end{figure}

To investigate this further we performed downsampling experiments.
Using the mutation signatures obtained using all 14717 substitutions as a gold standard, 
we assessed performance of the proposed method on down-sampled data consisting of $r\%$ of the original data, where  $r=(1\%, 2.5\%, 5\%, 10\%, 25\%, 50\%)$.
To measure robustness we used the cosine similarity on the 
full dimensional vector space, which allows comparison between the full model and the independent model.
We repeated each down-sampling experiment 100 times for each model.

@@

To provide a more comprehensive practical illustration of
our method, we applied it to somatic mutation data from 30 cancer types \cite{pmid23945592}.
We applied the method to each cancer type separately to assess similarity of estimated signatures across cancer types.
For each cancer type we selected the number of signatures $K$ by fitting the model with increasing $K$ and examining the log-likelihood, bootstrap errors, and correlation of membership parameters.The selected values of $K$ are given in S2 Table.
Also, we simply removed somatic mutations located in an intergenic region to include transcription strand biases as mutation features.
Finally, we merged similar mutation signatures across different cancer types 
(when their Frobenius Distance were $<$ $0.6$). 
% XXX WHAT KIND OF CLUSTERING?
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).

>>>>

Cancer is a genomic disease. 
As we lead a life, DNA within our cells acquires random somatic mutations,
mainly caused by DNA replication errors and exposures to mutagens such as chemical substances, radioactivities and inflammatory reactions.  
Although most mutations are harmless (called ``passenger mutations''), 
a small portions of mutations at some specific sites in cancer genes (``driver mutations'') 
%confer growth activities to the cells over other cells,
affect cell growth,
causing autonomous proliferation, tissue invasion, and contributing to oncogenesis \cite{stratton2009cancer}.
Cancer genome studies typically focus on identifying driver mutations, 
to help understand the mechanism of cancer development.
However, passenger mutations can also yield important information, 
because they often show patterns (``mutation signatures'') which 
can provide insights into the forces that cause somatic mutations.
%Classical analyses of mutation patterns have revealed a number of relationships between mutation patterns and carcinogens.
For example, classical studies of mutation patterns
revealed that C $>$ A mutations are abundant in lung cancers in patients with smoking history,
and these are caused by benzo(a)pyrene included in tobacco smoke \cite{pmid12379884}.
Also, C $>$ T and CC $>$ TT  mutations are abundant in ultraviolet-light-associated skin cancers, 
and these are caused by pyrimidine dimers as a result of ultraviolet radiation \cite{pmid15748635}.

@@

The inferred APOBEC signature under the independent model
shows a clear depletion of G base at the $-2$ position,
which is consistent to the previous study \cite{pmid23318258} and results in the next subsection (Figs. 3A and 3B).
In contrast, for the full model, this tendency is rather mild (Figs. 3C, 3D and S1).
The inferred AA mutation signature has no clear characteristics at the $-2$ position.
These results suggest that our independent model has the potential
to identify signatures in more detail and with less data than existing approaches based on the full model.

\begin{figure}[h]
\caption{{\bf The mutation signatures for the UCUT data, and the results of down-sampling experiments.}
3072 elements in the full model mutation signatures were shown divided by 6 substitution patterns and strand directions.
(A, B) APOBEC and AA signature for the independent model.
(C, D) APOBEC and AA signature for the full model.
(E, F) APOBEC and AA signature stability (the mean cosine similarity for each down-sampling ratio).}
\label{UCUT}
\end{figure}

To investigate this further we performed down-sampling experiments.
Using the mutation signatures obtained using all 14717 substitutions as a gold standard, 
we assessed performance of the proposed method on down-sampled data consisting of $r\%$ of the original data, where  $r=(1\%, 2.5\%, 5\%, 10\%, 25\%, 50\%)$.
To measure robustness we used the cosine similarity on the 
full dimensional vector space, which allows comparison between the full model and the independent model.
We repeated each down-sampling experiment 100 times for each model.

@@

To provide a more comprehensive practical illustration of
our method, we applied it to somatic mutation data from 30 cancer types \cite{pmid23945592}.
We applied the method to each cancer type separately to assess similarity of estimated signatures across cancer types.
For each cancer type we selected the number of signatures $K$ by fitting the model with increasing $K$ and examining the log-likelihood, bootstrap errors, and correlation of membership parameters.
The selected values of $K$ are given in S2 Table.
Also, we simply removed somatic mutations located in an intergenic region to include transcription strand biases as mutation features.
Finally, we merged similar mutation signatures across different cancer types 
(when their Frobenius Distance were $<$ $0.6$). 
% XXX WHAT KIND OF CLUSTERING?
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).
